Probabilistic Forecast Reconciliation

### 2018-11-13 Presentation/ProbForeRec.tex
finalised talk

  	\item Gross Domestic Product

@@

  \begin{frame}{With a sample}
  		\item Often densities are unavailable but we can simulate a sample from the predictive distribution.
  		\item Suppose $\bm{\hat{y}}_{T+h}^{[1]},\ldots,\bm{\hat{y}}_{T+h}^{[J]}$ is a sample from the unreconciled probabilistic forecast.
  		\item Then setting $\tilde{\bm y}_{T+h}^{[j]}=\bm{S}\bm{G}\hat{\bm y}_{T+h}^{[j]}$ produces a sample from the reconciled distribution with respect to $g$.

@@

@@

>>>>

  	\item Gross Domestic Product \hyperlink{GDP}{\beamerbutton{}}

@@

%  \begin{frame}{With a sample}
%  		\item Often densities are unavailable but we can simulate a sample from the predictive distribution.
%  		\pause
%  		\item Suppose $\bm{\hat{y}}_{T+h}^{[1]},\ldots,\bm{\hat{y}}_{T+h}^{[J]}$ is a sample from the unreconciled probabilistic forecast.
%  		\pause
%  		\item Then setting $\tilde{\bm y}_{T+h}^{[j]}=\bm{S}\bm{G}\hat{\bm y}_{T+h}^{[j]}$ produces a sample from the reconciled distribution with respect to $g$.

@@

  \begin{frame}{GDP}\label{GDP}
\includegraphics[height=7cm]{Figs/GDP}

@@

  	\item Use disaggregate series as predictors (although we can).
